---
output: github_document
html_preview: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# cccharts

<div id="devex-badge"><a rel="Exploration" href="https://github.com/BCDevExchange/docs/blob/master/discussion/projectstates.md"><img alt="Being designed and built, but in the lab. May change, disappear, or be buggy." style="border-width:0" src="https://assets.bcdevexchange.org/images/badges/exploration.svg" title="Being designed and built, but in the lab. May change, disappear, or be buggy." /></a>[![Travis-CI Build Status](https://travis-ci.org/bcgov/cccharts.svg?branch=master)](https://travis-ci.org/bcgov/cccharts)</div>
  

## Overview

`cccharts` is an R package to plot climate change indicator data for British Columbia.
It is essentially a wrapper on top of `ggplot2` code.

## Installation

The package is not available on CRAN, but can be installed from GitHub using the [devtools](https://github.com/hadley/devtools) package: 
```
# install.packages("devtools")
devtools::install_github("bcgov/cccharts")
```

## Features

### Three Plot Types

`cccharts` produces three types of plots:

- Color-coded point (or bar chart) estimates with upper and lower confidence intervals (if available) (`plot_estimates`).
- Color-coded maps of B.C. with the estimates for Ecoprovinces or Stations (`map_estimates`).
- Raw data with estimated trend lines (`plot_fit`).

Examples of the three types of plots are presented below.

To get more information on the arguments that a function takes type for example `?plot_estimates`.

### PNG Files and `ggplot` Objects

The three base functions return `ggplot` objects which can be modified prior to plotting.
The higher level wrappers `plot_estimates_pngs`, `map_estimates_pngs` etc
automatically save the plots to png files in a subdirectory of the folder `cccharts` in
the working directory. 
They also return a list of the `ggplot` objects in case the users wishes to manipulate them further.

### Color Scheme

The default color scheme is a *diverging* BrBG Brewer [palette](http://colorbrewer2.org/#type=diverging&scheme=BrBG&n=11).
The user can override the color scheme for the `plot_estimates` or `map_estimates` functions by setting the `low`, `mid`, and `high` arguments.
To switch to a *sequential* color scheme simply set `mid = NULL`.
To make all points the same color (and suppress a color legend) simply set `low` and `high` at the same value.

### Data

`cccharts`pulls climate change indicator data from the [BC Data Catalogue ](https://catalogue.data.gov.bc.ca/dataset?download_audience=Public). The source data sets are licensed under the [Open Government License - British Columbia](http://www2.gov.bc.ca/gov/content?id=A519A56BC2BF44E4A008B33FCF527F61).

Type `data()` to see the available datasets or for example type `?snow`
for more information on the snow data.

## Usage

```{r, fig.width=8, fig.height=8}
library(cccharts)
plot_estimates(data = cccharts::sea_surface_temperature_station, x = "Season", facet = "Station")
```

```{r, fig.width=8, fig.height=8}
map_estimates(data = cccharts::sea_level_station, station = TRUE, bounds = c(0.1,0.7,0,0.55))
```

```{r, fig.width=8, fig.height=5}
plot_fit(data = dplyr::filter(cccharts::flow_station_discharge, Term == "Medium", Statistic == "Mean", Season == "Annual"), observed = cccharts::flow_station_discharge_observed, free_y = TRUE, facet = "Station")
```

To generate the plot files (creates a folder in the working directory called `cccharts`).
```
library(cccharts)
demo("cccharts", ask = FALSE)
```

## Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/bcgov/rcaaqs/issues/).

## How to Contribute

If you would like to contribute to the package, please see our [CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.


## License

    Copyright 2016 Province of British Columbia

    Licensed under the Apache License, Version 2.0 (the "License");
    you may not use this file except in compliance with the License.
    You may obtain a copy of the License at 

       http://www.apache.org/licenses/LICENSE-2.0

    Unless required by applicable law or agreed to in writing, software
    distributed under the License is distributed on an "AS IS" BASIS,
    WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
    See the License for the specific language governing permissions and
    limitations under the License.


This repository is maintained by [Environmental Reporting BC](http://www2.gov.bc.ca/gov/content?id=FF80E0B985F245CEA62808414D78C41B). Click [here](https://github.com/bcgov/EnvReportBC-RepoList) for a complete list of our repositories on GitHub.

